% !Mode:: "TeX:UTF-8"

\begin{chineseabstract}

高校体测工作长期依赖纸质记录和电子表格，学生人数多、录入时间紧、评分规则固定、核对量大。管理人员和教师需要在短时间内完成数据采集、成绩换算、结果查询和简要分析。针对这些问题，本文提出一种将规则计算与大模型辅助分析结合的智能分析方法，并实现了一个完整系统。系统覆盖体测记录维护、课程管理、成绩计算、统计分析、请假审批和学生自助查询，同时借助 AI 能力辅助解释体测结果和回答数据问题。

系统从高校体测管理场景出发，划分了用户与角色管理、课程与体测记录管理、成绩计算与导出、AI 分析、操作日志追踪和学生端服务等模块。系统采用前后端分离结构，后端处理业务逻辑、权限控制、数据访问和模型调用，前端负责页面展示、表单交互和图表呈现。

实现中重点解决了批量导入导出、多角色权限隔离、课程状态控制、请假审批留痕和 AI 分析证据组织等问题。数据库结构、服务端校验和操作日志共同支撑日常教学场景下的主要业务。功能测试和关键链路验证表明，系统在登录认证、数据维护、成绩计算、权限控制、AI 分析和问答等方面达到了预期要求。

本文实现的系统能够支撑高校体测管理中的后台维护、教师录入、学生查询、请假审批和智能辅助分析，为大学生体质健康管理信息化提供了一套可落地的方案。

\chinesekeyword{大学生体质健康智能分析系统；SpringBoot 3.3；Spring AI；MyBatis-Plus；Vue3；前后端分离；SpringSecurity}
\end{chineseabstract}

\begin{englishabstract}

As educational informatization advances, university physical fitness management can no longer rely on paper records and scattered spreadsheets. Fitness testing involves large student cohorts, short entry windows, fixed scoring rules, and frequent verification. Administrators and teachers must complete data collection, score conversion, result lookup, and analysis within a limited period. To address these needs, this thesis designs and implements a university students' physical fitness intelligent analysis system based on SpringBoot 3.3, MyBatis-Plus, SpringSecurity, Vue3, and Spring AI. The system serves administrators, teachers, and students, covering fitness record management, course management, score calculation, statistical analysis, leave approval, student inquiry, and AI-assisted result interpretation.

Starting from real university fitness testing scenarios, this study defines modules for user and role management, course and fitness record management, score calculation and export, AI analysis, operation log tracking, and student-side services. The system adopts a front-end/back-end separation architecture. The backend handles business processing, permission control, data access, and model invocation, while the frontend manages page display, form interaction, and chart presentation. AI functions are integrated through Spring AI and generate analysis grounded in business data stored in the system.

During implementation, this thesis focuses on batch import and export, multi-role permission isolation, data consistency in concentrated entry scenarios, course status control, leave approval traceability, and AI evidence organization. Database design, server-side validation, import verification, and operation logging support the main business processes in routine teaching scenarios. Functional testing and key workflow verification show that the system meets expected requirements in login authentication, data maintenance, score calculation, permission control, AI analysis, and question answering.

Overall, the implemented system provides relatively complete business functions and a clear interaction process. It supports administrative maintenance, teacher-side data entry, student inquiry, leave approval, and intelligent analysis, offering a practical solution for the informatization and intelligent development of university physical fitness management.

\englishkeyword{University Students' Physical Fitness Intelligent Analysis System; SpringBoot 3.3; Spring AI; MyBatis-Plus; Vue3; Front-End/Back-End Separation; SpringSecurity}
\end{englishabstract}
